---
title: "A Markov Text Model"
Author: Yile Shi, Letian Yin, Danni Chen
Date: 29th Sep 2021
output:
  pdf_document: default
  html_notebook: default
---
#Change working dictionary and read file to R
```{r}
setwd("E:/Edi/StP/StP-practical_1-Gourp_8")
Bible <- scan(file = "Bible.txt", what = "character", skip = 156)
n_Bible <-length(Bible)
Bible <- Bible[-((n_Bible - 2909) : n_Bible)] ## strip license
Sys.setlocale('LC_ALL','C')
```
#create function split_punct() to seperate punctuation marks and words
```{r}
split_punct <- function(vec){
  index_punct <- NULL
  punct <- c(",", ".", ";", "!", ":", "?")
  n_index = NULL
  for (i in 1 : length(punct)) {
    index_punct[[i]]<- grep(punct[i], vec, fixed = TRUE)
    n_index[i] = length(index_punct[i])
  }
  n_index
  return(index_punct)
}
```

```{r}
split_punct(Bible)
```








Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
